A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Add in figure to the paper
Font changes
Add in hardware randomness blurb

\begin{document}
\maketitle
\doublespace

@@

 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{randstring.pdf}
   \caption{Random string performance}
   \label{fig:randstring}
 \end{figure}
 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{seqstring.pdf}
   \caption{Sequential string performance}
   \label{fig:seqstring}
 \end{figure}

@@

>>>>

\begin{document}
\maketitle
%\doublespace

@@

 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{randstring.pdf}
   \caption{Random string performance}
   \label{fig:randstring}
 \end{figure}
 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{seqstring.pdf}
   \caption{Sequential string performance}
   \label{fig:seqstring}
 \end{figure}
 \begin{figure}[H]
   \centering
   \includegraphics[width=4in]{chainlength.pdf}
   \caption{Simple tabulation hashing decreases the average chain length}
   \label{fig:seqstring}
 \end{figure}

@@

Given the strong performance of simple tabulation hashing and the only downside
being the cost of memory lookups, processor manufacturers should look into
adding random tables into hardware as a ROM.  We found that for what we found
optimal for Python, we only needed 16KB of randomness.  This would be a trivial
cost in ROM given that processors have MBs of higher level caches nowadays.
